\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2013-12-15 paper/paper.tex
Cut rambling para, add transition

\texttt{Graphics.Input} does not currently support radio buttons, but one could
imagine them being added in a way similar to the others. However, it is worth
observing that the pattern itself leaves something to be desired, namely, that
the functions are impure. One can apply \texttt{hoverable} to an Element twice,
place the resulting Elements in in different places on the screen (or place one
not at all), and the signals of Booleans will be different. This is true,
analogously, of all the functions of similar type in the library. We know of no
alternative that has been proposed, and do not have one ourselves. However, we
point out this deficiency in order to illustrate that the library still has room
for incremental and perhaps even radical growth.

@@

A menu can be thought of as an instance of a tree.

>>>>

@@

Having established the need for \texttt{hoverablesJoin} and implementing it, we
now turn to stated task of creating menus. A menu can be thought of as an
instance of a tree.
